The \kplr\ Catalog: Systematic probabilistic parameter estimation for every \kepler\ planet candidate

### 2013-12-27 document/ms.tex
NYU HPC ack
swift ack
starting to describe integration method

\acknowledgments
It is a pleasure to thank
    Tom Barclay (NASA Ames),
    Tim Morton (Princeton),
    \ldots
for helpful contributions to the ideas and code presented here.
This project was partially supported by the NSF (grant AST-0908357), and NASA
(grant NNX08AJ48G).

@@

>>>>

\acknowledgments
It is a pleasure to thank
    Tom Barclay (NASA Ames),
    Tim Morton (Princeton),
    Jon Swift (Caltech),
    \ldots
for helpful contributions to the ideas and code presented here.
This work made use of the BuTinah cluster supported by NYU HPC (FIXME).
This project was partially supported by the NSF (grant AST-0908357), and NASA
(grant NNX08AJ48G).

@@

\appendix

\section{Recursive exposure time integration}

It is well known (Kipping, others, ASK BARCLAY) that integrating the
exposure time when computing a generative light curve model makes a huge
difference especially for short period orbits.
Kipping argues for the use of a resampling technique.
For computational efficiency and robustness to \emph{contact point
discontinuities}, we developed and used an adaptive recursive algorithm.
This algorithm refines the resampling grid around points where where second
derivative of the light curve function is largest.
This means that the base grid can be extremely coarse.

The basic idea is that we have some function $f(t)$ that returns the
instantaneous flux of the system at time $t$ but we would like to compute the
integrated flux over an exposure time \texp
\begin{eqnarray}
f_\mathrm{int}(t_0) &=& \int_{t_0-\texp/2}^{t_0+\texp/2} f(t) \dd t
\end{eqnarray}
